Manuscript plots

### 2023-11-22 manuscript_modelling_and_plots.Rmd
new figs and associated code

# creating state spaces - cuts the x and y coordinates into 3 degree chunks 
example.fixation <- example.fixation %>%
  dplyr::mutate(x_range = cut(yaw, seq(minX, maxX, by = 3), right = FALSE)) %>%
  dplyr::mutate(y_range = cut(pitch, seq(minX, maxY, by = 3), right = FALSE))

@@

```{r}
## fit 3 random n-back slope for sigma
sge.fit.3 <- brm(data = entropy.total %>%
                   tidyr::drop_na() %>%
                   dplyr::filter(ppid != 34, ppid != 39, ppid != 47),
                 family = gaussian(),
                 bf(e.norm ~ n_back * lead + (1 + n_back | ppid), sigma ~ n_back * lead + (1 + n_back | ppid)),
                 prior = c(prior(normal(.5, .2), class = Intercept),
                           prior(normal(-.1, .2), class = b, coef = "n_backTRUE"),
                           prior(normal(0, .2), class = b, coef = "leadTRUE"),
                           prior(normal(0, .2), class = b, coef = "n_backTRUE:leadTRUE"),
                           prior(normal(0, .5), class = b, dpar = "sigma", coef = "n_backTRUE"),
                           prior(normal(0, .5), class = b, dpar = "sigma", coef = "leadTRUE"),
                           prior(normal(0, .5), class = b, dpar = "sigma", coef = "n_backTRUE:leadTRUE"),
                           prior(cauchy(0, 2), class = sd),
                           prior(lkj(2), class = cor)),
                                   iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13)
print(summary(sge.fit.3), digits = 5)

@@

# posterior distribution for the beta_N parameter i.e. the average change in stationary gaze entropy without a lead vehicle and in the presence of n-back
beta_n <- sge.fit.3 %>%
  spread_draws(b_n_backTRUE) %>%
  ggplot(aes(x = b_n_backTRUE)) +
  stat_halfeye(.width = c(.5, .95)) +
  geom_vline(mapping = aes(xintercept = 0), linetype = "dashed") +
  ylab("") +
  xlab(expression(italic(p(beta[N] ~ "|" ~ italic(E))))) +
  xlim(-.16, 0) +
  theme_plot +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), title = element_text(size = 7), legend.title = element_text(size = 11), legend.text = element_text(size = 10))

# posterior distribution for the beta_L parameter i.e. average change in stationary gaze entropy when a lead vehicle is present (without n-back)
beta_l <- sge.fit.3 %>%
  spread_draws(b_leadTRUE) %>%
  ggplot(aes(x = b_leadTRUE)) +
  stat_halfeye(.width = c(.5, .95)) +
  geom_vline(mapping = aes(xintercept = 0), linetype = "dashed") +
  ylab("") +
  xlab(expression(italic(p(beta[L] ~ "|" ~ italic(E))))) +
  scale_x_continuous(limits = c(-.05, 0), breaks = c(-.04, -.02, 0)) +
  theme_plot +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), title = element_text(size = 7), legend.title = element_text(size = 11), legend.text = element_text(size = 10))

# posterior distribution for beta_NL parameter i.e. interaction between n-back and lead vehicle. 
beta_nl <- sge.fit.3 %>%
  spread_draws(`b_n_backTRUE:leadTRUE`) %>%
  ggplot(aes(x = `b_n_backTRUE:leadTRUE`)) +
  stat_halfeye(.width = c(.5, .95)) +
  geom_vline(mapping = aes(xintercept = 0), linetype = "dashed") +
  ylab("") +
  xlab(expression(italic(p(beta[NL] ~ "|" ~ italic(E))))) +
  xlim(-.02, .04) +
  theme_plot +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), title = element_text(size = 7), legend.title = element_text(size = 11), legend.text = element_text(size = 10))

# combinding plots into one big plot 
sge.plot <- (beta_0 | beta_n) / (beta_l | beta_nl)

@@

# beta_0
alpha_0 <- sge.fit.3 %>%
  spread_draws(b_sigma_Intercept) %>%
  ggplot(aes(x = b_sigma_Intercept)) +
  stat_halfeye(.width = c(.5, .95)) +
  ylab("") +
  scale_x_continuous(limits = c(-3.4, -2.7), labels = label_number(accuracy = 0.01)) +
  xlab(expression(italic(p(alpha[0] ~ "|" ~ italic(E))))) +
  theme_plot +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), title = element_text(size = 7), legend.title = element_text(size = 11), legend.text = element_text(size = 10))

@@

# posterior conditional means for n-back/no n-back and posterior predictive intervals
posterior.mean.intervals.sge <- entropy.total %>%
  tidyr::drop_na() %>%
  dplyr::filter(ppid != 34, ppid != 39, ppid != 47) %>%
  ggplot(aes(x = e.norm, y = n_back)) +
  stat_pointinterval(aes(x = .epred), data = means, .width = c(.50, .95), position = position_nudge(y = -0.3)) +
  stat_interval(aes(x = .prediction), data = preds, .width = c(.50, .80, .95, .99)) +
  geom_jitter(data = entropy.total %>%
  tidyr::drop_na() %>%
  dplyr::filter(ppid != 34, ppid != 39, ppid != 47), height = .03, alpha = .2) +
  scale_y_discrete(labels = c('No N-back','N-back')) +
  scale_color_brewer("Posterior predictive interval") +
  xlab(expression("Predicted" ~ italic(H[s]))) +
  ylab("Secondary task") +
  scale_x_continuous(breaks = seq(0, .6, .1), labels = label_number(accuracy = 0.01)) +
  facet_wrap(~ lead, labeller = labeller(lead = l.labs),  ncol = 1) +
  theme_plot +
  theme(legend.position = c(.5, .95), legend.direction = "horizontal", legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), title = element_text(size = 7), legend.title = element_text(size = 11), legend.text = element_text(size = 10))

@@

# computes strip plot of the individual effects alongside the average, the credible intervals, and heterogenity intervals
HI_effect_2_back_plot <- ggplot() +
  geom_jitter(ppid.effects, mapping = aes(x = x, y = ranef), width = 0.01, height = 0, size = 4,
              shape = 21, colour = "black", fill = viridis(5)[3], alpha = .95, stroke = 1) +
  theme_plot +
  scale_y_continuous(breaks = round(seq(-.3, .3, 0.05), digits = 2)) +
  ylab(expression("N-back effect on" ~ mu ~ "of" ~ italic(H[s]) ~ "(% point units)")) +
  xlab("") + 
  geom_hline(aes(yintercept = bayes.credible.intervals$`l-95% CI`[3], linetype ="95% CI"), size = 1.5,  color = viridis(5)[3]) +
  geom_hline(aes(yintercept = bayes.credible.intervals$`u-95% CI`[3], linetype="95% CI"), size = 1.5,  color = viridis(5)[3]) +
  geom_hline(aes(yintercept = summary(sge.fit.3)[["fixed"]][3,1], linetype = "beta_1"), size = 1.5, color = "black") +
  geom_hline(aes(yintercept = summary(sge.fit.3)[["fixed"]][3,1] + 1.96 * ran.effects, linetype = "95% HI"), size = 1.5, color = viridis(5)[2]) +
  geom_hline(aes(yintercept = summary(sge.fit.3)[["fixed"]][3,1] - 1.96 * ran.effects, linetype = "95% HI"), size = 1.5, color = viridis(5)[2]) +
  scale_linetype_manual(name = " ", values = c(2, 1, 1), labels = c("95% CI", "95% HI", expression(beta[N])), guide = guide_legend(override.aes = list(color = c(viridis(5)[3], viridis(5)[2], "black")))) +
  scale_fill_manual(name = "Parameter", values = c(viridis(5)[2])) +
  theme(legend.position = c(.22, .85), legend.key = element_blank(), legend.key.width = unit(0.2, 'cm'), axis.text.y = element_blank(), axis.ticks.y = element_blank(), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), title = element_text(size = 7), legend.title = element_text(size = 11), legend.text = element_text(size = 10)) +
  coord_flip()

@@

summary(sge.fit.3)[["fixed"]][3,1] + 1.96 * ran.effects
summary(sge.fit.3)[["fixed"]][3,1] - 1.96 * ran.effects
```

@@

# plotting the distribution for people who would follow average trends
proportion_pop_2_back <- densplot + 
  geom_area(data = subset(densplot_dat, x < 0), aes(x=x, y=y), fill = viridis(5)[2], alpha = .4, color = viridis(5)[2]) +
  xlab(expression("N-back effect on" ~ mu ~ "of" ~ italic(H[s]) ~ "(% point units)")) +
  ylab("") +
  scale_x_continuous(limits = c(-.4, .25), expand = c(0, 0), labels = label_number(accuracy = 0.01)) +
  scale_y_continuous(limits = c(0, 6.5), expand = c(0, 0)) +
  theme_plot +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), title = element_text(size = 7), legend.title = element_text(size = 11), legend.text = element_text(size = 10)) 
signif(area, digits=2) * 100

@@

summary(gte.fit.6)
describe_posterior(gte.fit.6)
```

@@

# beta_N
beta_n <- gte.fit.6 %>%
  spread_draws(b_n_backTRUE) %>%
  ggplot(aes(x = b_n_backTRUE)) +
  stat_halfeye(.width = c(.5, .95)) +
  geom_vline(mapping = aes(xintercept = 0), linetype = "dashed") +
  ylab("") +
  xlab(expression(italic(p(beta[N] ~ "|" ~ italic(E))))) +
  scale_x_continuous(limits = c(-.045, .02), breaks = c(-.04, -.02, 0, .02),labels = label_number(accuracy = 0.01)) +
  theme_plot +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), title = element_text(size = 7), legend.title = element_text(size = 11), legend.text = element_text(size = 10))

# beta_L
beta_l <- gte.fit.6 %>%
  spread_draws(b_leadTRUE) %>%
  ggplot(aes(x = b_leadTRUE)) +
  stat_halfeye(.width = c(.5, .95)) +
  geom_vline(mapping = aes(xintercept = 0), linetype = "dashed") +
  ylab("") +
  xlab(expression(italic(p(beta[L] ~ "|" ~ italic(E))))) +
  scale_x_continuous(limits = c(-.004, .006), breaks = c(-.003, 0, .003)) +
  theme_plot +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), title = element_text(size = 7), legend.title = element_text(size = 11), legend.text = element_text(size = 10))

# beta_NL
beta_nl <- gte.fit.6 %>%
  spread_draws(`b_n_backTRUE:leadTRUE`) %>%
  ggplot(aes(x = `b_n_backTRUE:leadTRUE`)) +
  stat_halfeye(.width = c(.5, .95)) +
  geom_vline(mapping = aes(xintercept = 0), linetype = "dashed") +
  ylab("") +
  xlab(expression(italic(p(beta[NL] ~ "|" ~ italic(E))))) +
  xlim(-.012, .004) +
  theme_plot +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), title = element_text(size = 7), legend.title = element_text(size = 11), legend.text = element_text(size = 10))

@@

# beta_0
alpha_0 <- gte.fit.6 %>%
  spread_draws(b_sigma_Intercept) %>%
  ggplot(aes(x = b_sigma_Intercept)) +
  stat_halfeye(.width = c(.5, .95)) +
  ylab("") +
  scale_x_continuous(limits = c(-5.1, -4), breaks = c(-5, -4.7, -4.4, -4.1),labels = label_number(accuracy = 0.01)) +
  xlab(expression(italic(p(alpha[0] ~ "|" ~ italic(E))))) +
  theme_plot +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), title = element_text(size = 7), legend.title = element_text(size = 11), legend.text = element_text(size = 10))

@@

# posterior conditional means for n-back/no n-back and posterior predictive intervals
posterior.mean.intervals.gte <- entropy.total %>%
  tidyr::drop_na() %>%
  dplyr::filter(ppid != 34, ppid != 39, ppid != 47) %>%
  ggplot(aes(x = gte.norm, y = n_back)) +
  stat_pointinterval(aes(x = .epred), data = means, .width = c(.50, .95), position = position_nudge(y = -0.3)) +
  stat_interval(aes(x = .prediction), data = preds, .width = c(.50, .80, .95, .99)) +
  geom_jitter(data = entropy.total %>%
  tidyr::drop_na() %>%
  dplyr::filter(ppid != 34, ppid != 39, ppid != 47), height = .03, alpha = .2) +
  scale_y_discrete(labels = c('No N-back','N-back')) +
  scale_color_brewer("Posterior predictive interval") +
  xlab(expression("Predicted" ~ italic(H[t]))) +
  ylab("Secondary task") +
  scale_x_continuous(breaks = seq(0, .2, .05)) +
  facet_wrap(~ lead, labeller = labeller(lead = l.labs),  ncol = 1) +
  theme_plot +
  theme(legend.position = c(.5, .95), legend.direction = "horizontal", legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), title = element_text(size = 7), legend.title = element_text(size = 11), legend.text = element_text(size = 10))

>>>>

# creating state spaces - cuts the x and y coordinates into 3 degree chunks 
example.fixation <- example.fixation %>%
  dplyr::mutate(x_range = cut(yaw, seq(minX, maxX, by = 10), right = FALSE)) %>%
  dplyr::mutate(y_range = cut(pitch, seq(minX, maxY, by = 10), right = FALSE))

@@

```{r}
## fit 3 random n-back slope for sigma
sge.fit.3 <- brm(data = entropy.total %>%
                   tidyr::drop_na() %>%
                   dplyr::filter(ppid != 34, ppid != 39, ppid != 47),
                 family = gaussian(),
                 bf(e.norm ~ n_back * lead + (1 + n_back | ppid), sigma ~ n_back * lead + (1 + n_back | ppid)),
                 prior = c(prior(normal(.5, .2), class = Intercept),
                           prior(normal(-.1, .2), class = b, coef = "n_backTRUE"),
                           prior(normal(0, .2), class = b, coef = "leadTRUE"),
                           prior(normal(0, .2), class = b, coef = "n_backTRUE:leadTRUE"),
                           prior(normal(0, .5), class = b, dpar = "sigma", coef = "n_backTRUE"),
                           prior(normal(0, .5), class = b, dpar = "sigma", coef = "leadTRUE"),
                           prior(normal(0, .5), class = b, dpar = "sigma", coef = "n_backTRUE:leadTRUE"),
                           prior(cauchy(0, 2), class = sd),
                           prior(lkj(2), class = cor)),
                                   iter = 5000, warmup = 2000, chains = 2, cores = 2, seed = 13)

print(summary(sge.fit.3), digits = 5)
describe_posterior(sge.fit.3)

@@

# posterior distribution for the beta_N parameter i.e. the average change in stationary gaze entropy without a lead vehicle and in the presence of n-back
beta_n <- sge.fit.3 %>%
  spread_draws(b_n_backTRUE) %>%
  ggplot(aes(x = b_n_backTRUE)) +
  stat_halfeye(.width = c(.5, .95)) +
  geom_vline(mapping = aes(xintercept = 0), linetype = "dashed") +
  ylab("") +
  xlab(expression(italic(p(beta[N] ~ "|" ~ italic(E))))) +
  xlim(-.22, 0) +
  theme_plot +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), title = element_text(size = 7), legend.title = element_text(size = 11), legend.text = element_text(size = 10))

# posterior distribution for the beta_L parameter i.e. average change in stationary gaze entropy when a lead vehicle is present (without n-back)
beta_l <- sge.fit.3 %>%
  spread_draws(b_leadTRUE) %>%
  ggplot(aes(x = b_leadTRUE)) +
  stat_halfeye(.width = c(.5, .95)) +
  geom_vline(mapping = aes(xintercept = 0), linetype = "dashed") +
  ylab("") +
  xlab(expression(italic(p(beta[L] ~ "|" ~ italic(E))))) +
  scale_x_continuous(limits = c(-.08, 0), breaks = c(-.06, -.04, -.02, 0)) +
  theme_plot +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), title = element_text(size = 7), legend.title = element_text(size = 11), legend.text = element_text(size = 10))

# posterior distribution for beta_NL parameter i.e. interaction between n-back and lead vehicle. 
beta_nl <- sge.fit.3 %>%
  spread_draws(`b_n_backTRUE:leadTRUE`) %>%
  ggplot(aes(x = `b_n_backTRUE:leadTRUE`)) +
  stat_halfeye(.width = c(.5, .95)) +
  geom_vline(mapping = aes(xintercept = 0), linetype = "dashed") +
  ylab("") +
  xlab(expression(italic(p(beta[NL] ~ "|" ~ italic(E))))) +
  xlim(-.02, .06) +
  theme_plot +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), title = element_text(size = 7), legend.title = element_text(size = 11), legend.text = element_text(size = 10))

# combining plots into one big plot 
sge.plot <- (beta_0 | beta_n) / (beta_l | beta_nl)

@@

# beta_0
alpha_0 <- sge.fit.3 %>%
  spread_draws(b_sigma_Intercept) %>%
  ggplot(aes(x = b_sigma_Intercept)) +
  stat_halfeye(.width = c(.5, .95)) +
  ylab("") +
  scale_x_continuous(limits = c(-3.1, -2.25), labels = label_number(accuracy = 0.01)) +
  xlab(expression(italic(p(alpha[0] ~ "|" ~ italic(E))))) +
  theme_plot +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), title = element_text(size = 7), legend.title = element_text(size = 11), legend.text = element_text(size = 10))

@@

# posterior conditional means for n-back/no n-back and posterior predictive intervals
posterior.mean.intervals.sge <- entropy.total %>%
  tidyr::drop_na() %>%
  dplyr::filter(ppid != 34, ppid != 39, ppid != 47) %>%
  ggplot(aes(x = e.norm, y = n_back)) +
  stat_pointinterval(aes(x = .epred), data = means, .width = c(.50, .95), position = position_nudge(y = -0.3)) +
  stat_interval(aes(x = .prediction), data = preds, .width = c(.50, .80, .95, .99)) +
  geom_jitter(data = entropy.total %>%
  tidyr::drop_na() %>%
  dplyr::filter(ppid != 34, ppid != 39, ppid != 47), height = .03, alpha = .2) +
  scale_y_discrete(labels = c('No N-back','N-back')) +
  scale_color_brewer("Posterior predictive interval") +
  xlab(expression("Predicted" ~ italic(H[s]))) +
  ylab("Secondary task") +
  scale_x_continuous(breaks = seq(0, .8, .2), labels = label_number(accuracy = 0.01)) +
  facet_wrap(~ lead, labeller = labeller(lead = l.labs),  ncol = 1) +
  theme_plot +
  theme(legend.position = c(.5, .95), legend.direction = "horizontal", legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), title = element_text(size = 7), legend.title = element_text(size = 11), legend.text = element_text(size = 10))

@@

# computes strip plot of the individual effects alongside the average, the credible intervals, and heterogenity intervals
HI_effect_2_back_plot <- ggplot() +
  geom_jitter(ppid.effects, mapping = aes(x = x, y = ranef), width = 0.01, height = 0, size = 4,
              shape = 21, colour = "black", fill = viridis(5)[3], alpha = .95, stroke = 1) +
  theme_plot +
  scale_y_continuous(limits = c(-.35, .1), breaks = seq(-.3, .1, 0.1), labels = label_number(accuracy = 0.01)) +
  ylab(expression("N-back effect on" ~ mu ~ "of" ~ italic(H[s]) ~ "(% point units)")) +
  xlab("") + 
  geom_hline(aes(yintercept = bayes.credible.intervals$`l-95% CI`[3], linetype ="95% CI"), size = 1.5,  color = viridis(5)[3]) +
  geom_hline(aes(yintercept = bayes.credible.intervals$`u-95% CI`[3], linetype="95% CI"), size = 1.5,  color = viridis(5)[3]) +
  geom_hline(aes(yintercept = summary(sge.fit.3)[["fixed"]][3,1], linetype = "beta_1"), size = 1.5, color = "black") +
  geom_hline(aes(yintercept = summary(sge.fit.3)[["fixed"]][3,1] + 1.96 * ran.effects, linetype = "95% HI"), size = 1.5, color = viridis(5)[2]) +
  geom_hline(aes(yintercept = summary(sge.fit.3)[["fixed"]][3,1] - 1.96 * ran.effects, linetype = "95% HI"), size = 1.5, color = viridis(5)[2]) +
  scale_linetype_manual(name = " ", values = c(2, 1, 1), labels = c("95% CI", "95% HI", expression(beta[N])), guide = guide_legend(override.aes = list(color = c(viridis(5)[3], viridis(5)[2], "black")))) +
  scale_fill_manual(name = "Parameter", values = c(viridis(5)[2])) +
  theme(legend.position = c(.22, .85), legend.key = element_blank(), legend.key.width = unit(0.2, 'cm'), axis.text.y = element_blank(), axis.ticks.y = element_blank(), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), title = element_text(size = 7), legend.title = element_text(size = 11), legend.text = element_text(size = 10)) +
  coord_flip()

@@

# heterogenity intervals - what effects could we expect to see in the population
summary(sge.fit.3)[["fixed"]][3,1] + 1.96 * ran.effects
summary(sge.fit.3)[["fixed"]][3,1] - 1.96 * ran.effects
```

@@

# plotting the distribution for people who would follow average trends
proportion_pop_2_back <- densplot + 
  geom_area(data = subset(densplot_dat, x < 0), aes(x=x, y=y), fill = viridis(5)[2], alpha = .4, color = viridis(5)[2]) +
  xlab(expression("N-back effect on" ~ mu ~ "of" ~ italic(H[s]) ~ "(% point units)")) +
  ylab("") +
  scale_x_continuous(limits = c(-.6, .3), expand = c(0, 0), labels = label_number(accuracy = 0.01)) +
  scale_y_continuous(limits = c(0, 4), expand = c(0, 0)) +
  theme_plot +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), title = element_text(size = 7), legend.title = element_text(size = 11), legend.text = element_text(size = 10)) 
signif(area, digits=2) * 100

@@

print(summary(gte.fit.6), digits = 5)
describe_posterior(gte.fit.6)
```

@@

# beta_N
beta_n <- gte.fit.6 %>%
  spread_draws(b_n_backTRUE) %>%
  ggplot(aes(x = b_n_backTRUE)) +
  stat_halfeye(.width = c(.5, .95)) +
  geom_vline(mapping = aes(xintercept = 0), linetype = "dashed") +
  ylab("") +
  xlab(expression(italic(p(beta[N] ~ "|" ~ italic(E))))) +
  scale_x_continuous(limits = c(-.05, .02), breaks = c(-.04, -.02, 0, .02),labels = label_number(accuracy = 0.01)) +
  theme_plot +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), title = element_text(size = 7), legend.title = element_text(size = 11), legend.text = element_text(size = 10))

# beta_L
beta_l <- gte.fit.6 %>%
  spread_draws(b_leadTRUE) %>%
  ggplot(aes(x = b_leadTRUE)) +
  stat_halfeye(.width = c(.5, .95)) +
  geom_vline(mapping = aes(xintercept = 0), linetype = "dashed") +
  ylab("") +
  xlab(expression(italic(p(beta[L] ~ "|" ~ italic(E))))) +
  scale_x_continuous(limits = c(-.007, .009), breaks = c(-.005, 0, .005)) +
  theme_plot +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), title = element_text(size = 7), legend.title = element_text(size = 11), legend.text = element_text(size = 10))

# beta_NL
beta_nl <- gte.fit.6 %>%
  spread_draws(`b_n_backTRUE:leadTRUE`) %>%
  ggplot(aes(x = `b_n_backTRUE:leadTRUE`)) +
  stat_halfeye(.width = c(.5, .95)) +
  geom_vline(mapping = aes(xintercept = 0), linetype = "dashed") +
  ylab("") +
  xlab(expression(italic(p(beta[NL] ~ "|" ~ italic(E))))) +
  scale_x_continuous(limits = c(-.02, .01)) +
  theme_plot +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), title = element_text(size = 7), legend.title = element_text(size = 11), legend.text = element_text(size = 10))

@@

# beta_0
alpha_0 <- gte.fit.6 %>%
  spread_draws(b_sigma_Intercept) %>%
  ggplot(aes(x = b_sigma_Intercept)) +
  stat_halfeye(.width = c(.5, .95)) +
  ylab("") +
  scale_x_continuous(limits = c(-4.6, -3.7), breaks = c(-4.4, -4.2, -4, -3.8),labels = label_number(accuracy = 0.01)) +
  xlab(expression(italic(p(alpha[0] ~ "|" ~ italic(E))))) +
  theme_plot +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), axis.text.y = element_blank(), axis.ticks.y = element_blank(),axis.ticks = element_blank(), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), title = element_text(size = 7), legend.title = element_text(size = 11), legend.text = element_text(size = 10))

@@

# posterior conditional means for n-back/no n-back and posterior predictive intervals
posterior.mean.intervals.gte <- entropy.total %>%
  tidyr::drop_na() %>%
  dplyr::filter(ppid != 34, ppid != 39, ppid != 47) %>%
  ggplot(aes(x = gte.norm, y = n_back)) +
  stat_pointinterval(aes(x = .epred), data = means, .width = c(.50, .95), position = position_nudge(y = -0.3)) +
  stat_interval(aes(x = .prediction), data = preds, .width = c(.50, .80, .95, .99)) +
  geom_jitter(data = entropy.total %>%
  tidyr::drop_na() %>%
  dplyr::filter(ppid != 34, ppid != 39, ppid != 47), height = .03, alpha = .2) +
  scale_y_discrete(labels = c('No N-back','N-back')) +
  scale_color_brewer("Posterior predictive interval") +
  xlab(expression("Predicted" ~ italic(H[t]))) +
  ylab("Secondary task") +
 scale_x_continuous(limits = c(0, .3), breaks = seq(0, .4, .1), labels = label_number(accuracy = 0.01)) +
  facet_wrap(~ lead, labeller = labeller(lead = l.labs),  ncol = 1) +
  theme_plot +
  theme(legend.position = c(.5, .95), legend.direction = "horizontal", legend.key = element_blank(), legend.key.width = unit(0.3, 'cm'), legend.key.size = unit(0.1, 'cm'), plot.title = element_text(size = 7.5, face = "bold"), axis.title.x = element_text(size = 11), axis.text.x = element_text(size = 11), title = element_text(size = 7), legend.title = element_text(size = 11), legend.text = element_text(size = 10))
